---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?

##Results

##Graphical Results


# South Carolina

We will subset the data by sex to see if the drug is sex specific.
#South Carolina:Males
```{r}
ScarolinaM <- filter(Scarolina,sex=="M")
barchartGC(~infected + group, data=ScarolinaM, type="percent")
```
#South Carolina:Females
```{r}
ScarolinaF <- filter(Scarolina, sex=="F")
barchartGC(~infected + group, data=ScarolinaF, type="percent")
```
#South Carolina: Both
```{r}
barchartGC(~infected + group, data=Scarolina, type="percent")
```

# Central Africa

We will subset the data by sex to see if the drug is sex specific.
##Centeral Africa:Males
```{r}
cenAfricaM <- filter(cenAfrica,sex=="M")
barchartGC(~infected + group, data=cenAfricaM, type="percent")
```

#Central Africa: Females
```{r}
cenAfricaF <- filter(cenAfrica,sex=="F")
barchartGC(~infected + group, data=cenAfricaF, type="percent")
```
#Central Africa:Both
```{r}
barchartGC(~infected + group, data=cenAfrica, type="percent")
```

# Korea
We will subset the data by sex to see if the drug is sex specific.
#Korea: Males
```{r}
koreaM <- filter(korea,sex=="M")
barchartGC(~infected + group, data=koreaM, type="percent")
```

#Korea: Females
```{r}
koreaF <- filter(korea,sex=="F")
barchartGC(~infected + group, data=koreaF, type="percent")
```
#Korea: Both
```{r}
barchartGC(~infected + group, data=korea, type="percent")
```

#Numerical Results
#south Carolina 
#Females: 
```{r}
ScarolinaF_table <- xtabs(~infected + group, data = ScarolinaF)
rowPerc(ScarolinaF_table)
```
#Males:
```{r}
ScarolinaM_table <- xtabs(~infected + group, data = ScarolinaM)
rowPerc(ScarolinaM_table)
```
#Both: 
```{r}
Scarolina_table <- xtabs(~infected + group, data = Scarolina)
rowPerc(Scarolina_table)      
```

#Central Africa
#Females:
```{r}
cenAfricaF_table <- xtabs(~infected + group, data = cenAfricaF)
rowPerc(cenAfricaF_table)
```
#Males:
```{r}
cenAfricaM_table <- xtabs(~infected + group, data = cenAfricaM)
rowPerc(cenAfricaM_table)
```
#Both: 
```{r}
cenAfrica_table <- xtabs(~infected + group, data = cenAfrica)
rowPerc(cenAfrica_table)
```
#Korea:
#Females:
```{r}
koreaF_table <- xtabs(~infected + group, data = koreaF)
rowPerc(koreaF_table)
```
#Males:
```{r}
koreaM_table <- xtabs(~infected + group, data = koreaM)
rowPerc(koreaM_table)
```
#Both:
```{r}
korea_table <- xtabs(~infected + group, data= korea)
rowPerc(korea_table)
```

#Inferential Results
#South Carolina 
#Females: 
```{r}
chisqtestGC(ScarolinaF_table)
```

#Males: 
```{r}
chisqtestGC(ScarolinaM_table)
```
#Both: 
```{r}
chisqtestGC(Scarolina_table)
```
#Centeral Africa
#Females:
```{r}
chisqtestGC(cenAfricaF_table)
```
#Males:
```{r}
chisqtestGC(cenAfricaM_table)
```
#Both
```{r}
chisqtestGC(cenAfrica_table)
```
#Korea
#Females:
```{r}
chisqtestGC(koreaF_table)
```
#Males:
```{r}
chisqtestGC(koreaM_table)
```
#Both:
```{r}
chisqtestGC(korea_table)
```

#Introduction 




#Methods








